---
title: "Rap artist"
author: "Poonam Shah"
date: "4/14/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggrepel)


color_choice1 = "darkslategray4"
color_choice2= "indianred1"
color_choice3 = "yellow"
```



```{r }

rankings <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-04-14/rankings.csv')

```



```{r }
rankings %>%
  select(points, gender, year, artist) %>%
  filter(year %in% c("1990", "1991", "1992","1993",
                     "1994","1995", "1996", "1997", 
                     "1998","1999")) %>%
  slice(year, 1:20) %>%
  ggplot(aes(x=artist, y=points, fill=gender)) +
  geom_bar(stat="identity") +
  coord_flip()+
  labs(x="Artist", y="Total number of points awarded", title = "The 20 best 90's rap artist")+
  scale_fill_manual(values = c(color_choice2, color_choice1, color_choice3))+
  theme_classic() -> top_20_plot
  
print(top_20_plot)

ggsave("top_20_plot.png", top_20_plot)
```


```



This week tidy tuesday is working with the data set of the Best Rap artist. It was not my favotite dataset since there was not a lot that could have been done with the data set. The first plot is about the 20 best rap artist in the 90s. The second plot is a pie chart showing the percentage of rap arist based on gender. It was hard to figure out the pie chart. It is a good chart to show the huge gender rap in rap music. 
